### 2021-02-17 conclusionfutureworks.tex
More comments and editis

Static analysis is becoming increasingly important for complement dynamic analysis approaches in the process of mining Android sandboxes. New static analysis techniques, like tainted analysis algorithms can also supports test generator tools for construct sandboxes more  sophisticated. However, state-of-the-art of mining Android sandboxes explore set of sensitive API methods in a Android app, using test generation tools, and highlight limitations at static analysis to mine sandboxes, neglecting the complement that could be obtained with it. To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.

In this paper, we performed two studies. In the first we conducted a non-exact replication of Bao et al. work, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times. Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and a second moment we disables the Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis. At the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment. The results of the first experiment reveals that ignoring the Joker tool, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms. Enabling the Droidfax staTic analysis, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid). We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated. In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.

As future work, we plan to investigate other promising tools to enhance our data from previous executions. We will use the benchmark to test tools like Sapienz (a search-based test generation tool) \cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}. And we will search for other great tools used by academia and by the industry to be tested by the benchmark DroidXP.
Also, we will execute each of the tools used in this experiment without the benchmark. And, we will compare these results with this experiment's results. This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark droidXP has on its results.

>>>>

Mining sandboxes is a popular technique to isolate android applications to analyse their behavior and discover vulnerabilities. Currently most sandbox mining approaches use dynamic analysis and have been studied previously in detail by many including Boa et al. But the impact of static analysis on these mining approaches is unexplored currently. New static analysis techniques, like taint analysis algorithms can also support test generator tools to construct sandboxes.  \kn{The following sentence is completely not understandable. Consider splitting it. }However, state-of-the-art of mining Android sandboxes explore set of sensitive API methods in a Android app, using test generation tools, and highlight limitations at static analysis to mine sandboxes, neglecting the complement that could be obtained with it. To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.

In this paper, we performed two studies. In the first we conducted a non-exact replication of Bao et al. work, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times. Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis. For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment. The results of the first experiment reveals that ignoring the Joker tool \kn{Briefly mention what is joker tool prior to using the word}, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms. Enabling the Droidfax staTic analysis, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid). We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated. In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.

As future work, we plan to investigate other promising tools to enhance our data from previous executions. We will use the benchmark to test tools like Sapienz (a search-based test generation tool)~\cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}. And we will search for other great tools used by academia and by the industry to be tested by the benchmark DroidXP.
Also, we will execute each of the tools used in this experiment without the benchmark. And, we will compare these results with this experiment's results. This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark droidXP has on its results.

### 2021-02-17 results.tex
add a new command that refers to the Bao et al. study
More comments and editis

Our first study performed a non-exact replication of Bao et al work.
%\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again by disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of the execution. The columns Exec. (WS) and Exec. (WOS) 
show the number of malwares identified when executing each tool with the
support of the DroidFax static analysis algorithms(WS) and without the support
of DroidFax static analysis algorithms(WOS). \kn{I have changed the I and II to Ws and WOS because I and II makes it sound like we ran the experiments two times which we have not yet done. }The Improvement column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
\kn{Is this really improvement? Is this not "contribution" of droidfax. Improvement happens when an earlier approach detected malware without support of droidfax. Here 23\% of malwares are simply detected by the presence of droidfax (so IMO it should be impact or contribution) not improvement}
In the previous work~\cite{}, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that the impact of DroidFax to the results is significant in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for which DroidFax improves its performance by 100\% (as expected).
Next we discuss the result of each individual test generation tool.

@@

In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset. To this end we leverage the FlowDroid tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms. Regarding accuracy, the tainted analysis approach detected 58 out of the 96 pairs in our dataset (60,42\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).

@@

>>>>

Our first study performed a non-exact replication of the \blls.
%\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again by disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of the execution. The columns Exec. (WS) and Exec. (WOS) 
show the number of malwares identified when executing each tool with the
support of the DroidFax static analysis algorithms(WS) and without the support
of DroidFax static analysis algorithms(WOS). \kn{I have changed the I and II to Ws and WOS because I and II makes it sound like we ran the experiments two times which we have not yet done. }The Improvement column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
\kn{Is this really improvement? Is this not "contribution" of droidfax. Improvement happens when an earlier approach detected malware without support of droidfax. Here 23\% of malwares are simply detected by the presence of droidfax (so IMO it should be impact or contribution) not improvement}
In the previous work~\cite{}, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that the impact of DroidFax to the results is significant in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for which DroidFax improves its performance by 100\% (as expected).
Next we discuss the result of each individual test generation tool.

@@

In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset. To this end we leverage the FlowDroid tool, which tracks how sensitive information flows through the apps using taint analysis. Regarding accuracy, the taint analysis approach detected 58 out of the 96 pairs in our dataset (60,42\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the execution of the dynamic analysis tools without DroidFax support (WOS).

@@

\kn{What does "our" approach mean in the finding box. I thought we simply study the malware detection under various settings With/without Droidfax and now with flowdroid}
